HFI in RISC-V

### 2025-03-26 paper.tex
Current Progress 1

\section{Related Work}

Several alternate approaches have been developed over the years for fine-grained isolation involving hardware-assisted techniques. Some systems have proposed extensions to the page table metadata such as Donky \cite{Donky}, whi

>>>>

\subsection{Current Progress}
As of the writing of this paper, we have begun a simple modification to the existing RISC-V in QEMU.
Our work has started by creating a basic internal register called \textit{hfi\_status}, which serves as a flag bit for verifying whether HFI can be toggled on or off via our newly implemented instructions.

\section{Related Work}
Several alternate approaches have been developed over the years for fine-grained isolation involving hardware-assisted techniques. Some systems have proposed extensions to the page table metadata such as Donky \cite{Donky}, whi
